---
title: "Analyse Data Set Mobile Price"
output: html_notebook
---

Initialisation et import des données

```{r}
install.packages("tidyverse")
install.packages("pacman")

library(tidyverse)

fig <- function(width, heigth){
     options(repr.plot.width = width, repr.plot.height = heigth)
}

library(pacman)

pacman::p_load(pacman,dplyr, ggplot2, rio, gridExtra, scales, ggcorrplot, caret, e1071)
```


```{r}
names(dataSet)
```

Affichage du set de données.

Colonnes : battery_power, blue, clock_speed, dual_sim, fc, four_g,int_memory, m_dep, mobile_wt, n_cores, pc, px_height, px_width, ram, sc_h, sc_w, talk_time, three_g, touch_screen, wifi, price_range

battery_power:Total energy a battery can store in one time measured in mAh
blue:Has bluetooth or not
clock_speed:speed at which microprocessor executes instructions
dual_sim:Has dual sim support or not
fc:Front Camera mega pixels
four_g:Has 4G or not
int_memory:Internal Memory in Gigabytes
m_dep:Mobile Depth in cm
mobile_wt:Weight of mobile phone
n_cores:Number of cores of processor
pc:Primary Camera mega pixels
px_height:Pixel Resolution Height
px_width:Pixel Resolution Width
ram:Random Access Memory in Megabytes
sc_h:Screen Height of mobile in cm
sc_w:Screen Width of mobile in cm
talk_time:longest time that a single battery charge will last when you are
three_g:Has 3G or not
touch_screen:Has touch screen or not
wifi:Has wifi or not

```{r}
dim(dataSet)
class(dataSet)
head(dataSet)
sapply(dataSet, class)
```


```{r}
summary(dataSet)
```


```{r}
corr <- round(cor(dataSet), 8)
ggcorrplot(corr)
fig(18, 16)
```


