---
title: "Analyzing Data Set Mobile Price"
output: html_notebook
---

Initialization and import of data

```{r}
install.packages("tidyverse")
install.packages("pacman")
install.packages("dplyr")
install.packages("plotly")

library(tidyverse)

fig <- function(width, heigth){
     options(repr.plot.width = width, repr.plot.height = heigth)
}

library(pacman)

pacman::p_load(pacman,dplyr, ggplot2, rio, gridExtra, scales, ggcorrplot, caret, e1071)

dataSet <- read.csv('data/train.csv')
```


```{r}
names(dataSet)
```

Display of the set of data.

Columns : battery_power, blue, clock_speed, dual_sim, fc, four_g,int_memory, m_dep, mobile_wt, n_cores, pc, px_height, px_width, ram, sc_h, sc_w, talk_time, three_g, touch_screen, wifi, price_range

battery_power:Total energy a battery can store in one time measured in mAh
blue:Has bluetooth or not
clock_speed:speed at which microprocessor executes instructions
dual_sim:Has dual sim support or not
fc:Front Camera mega pixels
four_g:Has 4G or not
int_memory:Internal Memory in Gigabytes
m_dep:Mobile Depth in cm
mobile_wt:Weight of mobile phone
n_cores:Number of cores of processor
pc:Primary Camera mega pixels
px_height:Pixel Resolution Height
px_width:Pixel Resolution Width
ram:Random Access Memory in Megabytes
sc_h:Screen Height of mobile in cm
sc_w:Screen Width of mobile in cm
talk_time:longest time that a single battery charge will last when you are
three_g:Has 3G or not
touch_screen:Has touch screen or not
wifi:Has wifi or not
price_range: This is the target variable with value of 0(low cost), 1(medium cost), 2(high cost) and 3(very high cost).

```{r}
dim(dataSet)
class(dataSet)
head(dataSet)
sapply(dataSet, class)
```


```{r}
summary(dataSet)
```

Correlation plot showing the features that are the most linked between each others
```{r}
library(ggcorrplot)
corr <- round(cor(dataSet), 8)
ggcorrplot(corr)
fig(18, 16)
```


```{r}
str(dataSet)
```

Displaying the cell percentages of different features of the dataSet
```{r}
prop.table(table(dataSet$blue)) # cell percentages
prop.table(table(dataSet$dual_sim)) # cell percentages
prop.table(table(dataSet$four_g)) # cell percentages
prop.table(table(dataSet$three_g)) # cell percentages
prop.table(table(dataSet$touch_screen)) # cell percentages
prop.table(table(dataSet$wifi)) # cell percentages
```


Subplots using filtered dataSet showing the impact of the screen height and width on the mobile's price range
```{r}
library(ggplot2)
data = data.frame(Dimensions_in_cm = c(dataSet$sc_h, dataSet$sc_w), 
               Screen = rep(c("Height", "Width"), c(length(dataSet$sc_h), length(dataSet$sc_w))))
ggplot(data, aes(Dimensions_in_cm, fill = Screen)) + 
  geom_bar(position = 'identity', alpha = .6)
```

Comparing the impact of two features on the mobile's price range
```{r}
library(ggplot2)
library(gridExtra)
dataSet$price_range <- as.factor(dataSet$price_range)
p1 <-  ggplot(dataSet, aes(x=px_width, y = px_height, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "Pixel Resolution Height vs Pixel Resolution Width")
p2 <- ggplot(dataSet, aes(x=price_range, y = ram, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "RAM vs Price Range")
grid.arrange(p1, p2,nrow = 1)
fig(24, 20)
```

Comparing the impact of two features on the mobile's price range
```{r}
library(ggplot2)
library(gridExtra)
dataSet$price_range <- as.factor(dataSet$price_range)
p3 <- ggplot(dataSet, aes(x=price_range, y = int_memory, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "int_memory vs Price Range")
p4 <- ggplot(dataSet, aes(x=price_range, y = battery_power, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "Battery power vs Price Range")
grid.arrange(p3, p4,nrow = 1)
fig(24, 20)
```


Data classification depending on battery power, ram, memory, clock speed and number of cores
```{r}
library(ggplot2)
p <- ggplot(dataSet, aes(battery_power, ram, color = price_range))+
  geom_point()
p + stat_ellipse()
p <- ggplot(dataSet, aes(int_memory, ram, color = price_range))+
  geom_point()
p + stat_ellipse()
p <- ggplot(dataSet, aes(x = ram, y = ram, color = price_range))+
  geom_point()
p + stat_ellipse()

p <- ggplot(dataSet, aes(x = clock_speed, y = n_cores, color = price_range))+
  geom_point()
p
```


3D graphic 
```{r}
library(tidyverse)
library(plotly)

# Creating the graphic
p <- plot_ly(
  dataSet, x = dataSet$battery_power, y = dataSet$ram, z = dataSet$int_memory, 
  color = dataSet$price_range) %>%
  add_markers(size=1) %>%
  layout(
    scene = list(xaxis = list(title = 'Battery Power'),
        yaxis = list(title = 'Ram'),
        zaxis = list(title = 'Memoire interne'))
        )
p
```


Interquartile range of two features at a time
```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
#Battery_power IQR
firstQuantile <- quantile(dataSet$battery_power, 0.25)
thirdQuantile <- quantile(dataSet$battery_power, 0.75)
battery_powerIQR <- dataSet %>% filter(dataSet$battery_power > firstQuantile & dataSet$battery_power < thirdQuantile)
#Int Memory IQR
firstQuantile <- quantile(dataSet$int_memory , 0.25)
thirdQuantile <- quantile(dataSet$int_memory, 0.75)
int_memoryIQR <- dataSet %>% filter(dataSet$int_memory > firstQuantile & dataSet$int_memory < thirdQuantile)
#ram IQR
firstQuantile <- quantile(dataSet$ram , 0.25)
thirdQuantile <- quantile(dataSet$ram, 0.75)
ramIQR <- dataSet %>% filter(dataSet$ram > firstQuantile & dataSet$ram < thirdQuantile)

p2 <- ggplot(ramIQR, aes(x=price_range, y = ram, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "IQR RAM vs Price Range")

p3 <- ggplot(int_memoryIQR, aes(x=price_range, y = int_memory, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "IQR int memory vs Price Range")

p4 <- ggplot(battery_powerIQR, aes(x=price_range, y = battery_power, color=price_range)) +
  geom_boxplot(outlier.colour="red", outlier.shape=8,
               outlier.size=4) +
  labs(title = "IQR battery power vs Price Range")
grid.arrange(p2, p3, p4,nrow = 1)
fig(24, 20)
```

